### 2023-08-16 vesicle_code/docs/confinedMulti/multicomponent_vesicles.tex
worked on figures

\begin{table}[h]
  \centering
  \begin{tabular}{l|ccccc}
    \hline
    Floppy percentage & 0\% & 15\% & 25\% & 35\% & 45\% \\ 
    Time  (dimensionless) & 2.32 & 2.30 & 2.29 & 2.26 & 2.24 \\
    \hline
  \end{tabular}
  \caption{\label{tbl:contractingTimes} \small The time required for the
  vesicles to completely pass through the neck.}
\end{table}

\begin{figure}[h]
  \centering
  \includegraphics[width=\columnwidth]{figures/bendingContracting.pdf}
  \caption{\label{fig:bendingAll} \small The bending energy for a
  single-component vesicle (blue) and a multicomponent vesicle
  (red)--(black) with $\alpha = 0.5$. As the size of the floppy region
  increases, the maximum bending energy decreases.}
\end{figure}

@@

\begin{figure}[h]
  \centering
  \subfigimg[width=\columnwidth]{(a)}{figures/ContractingEnergy_SC.pdf}
  \subfigimg[width=\columnwidth]{(b)}{figures/ContractingEnergy_MC.pdf}
  \caption{\label{fig:bendingSC_contracting} \small The bending energy
  of (a) a single-component vesicle, and (b) a multicomponent vesicle
  whose boundary is 45\% floppy passing through a contracting geometry.
  The vesicle shape at different locations are included. We can clearly
  see that the sudden increases and decreases in the bending energy are
  due to transitions between lower energy and higher energy shapes.}
\end{figure}

>>>>

\begin{table}[h]
  \centering
  \begin{tabular}{l|cccccc}
    \hline
    Floppy percentage & 0\% & 15\% & 25\% & 35\% & 45\% & 50\% \\ 
    Dimensionless time & 2.32 & 2.30 & 2.29 & 2.26 & 2.23 & 2.25\\
    \hline
  \end{tabular}
  \caption{\label{tbl:contractingTimes} \small The time required for the
  vesicles to completely pass through the neck.}
\end{table}

\begin{figure}[h]
  \centering
  \includegraphics[width=\columnwidth]{figures/bendingContracting.pdf}
  \caption{\label{fig:bendingAll} \small The bending energies of the
  single-component and multicomponent vesicles in Figure~\ref{fig:RA5}.
  The vertical dashed lines correspond to the configurations in
  Figure~\ref{fig:RA5}. As the size of the floppy region increases, the
  maximum bending energy decreases.}
\end{figure}

@@

\begin{figure}[h]
  \centering
  \subfigimg[width=\columnwidth]{(a)}{figures/ContractingEnergy_SC.pdf}
  \subfigimg[width=\columnwidth]{(b)}{figures/ContractingEnergy_MC.pdf}
  \caption{\label{fig:bendingSC_contracting} \small The bending energy
  of (a) a stiff single-component vesicle, and (b) a multicomponent
  vesicle whose boundary is 45\% floppy passing through a contracting
  geometry. The vesicle shape at different locations are included. We
  can clearly see that the sudden increases and decreases in the bending
  energy are due to transitions between lower energy and higher energy
  shapes.}
\end{figure}
